The paper on \Large \bf Blockchain Frontrunning

### 2018-09-04 frontrunning/Latex/sections/paper.tex
[frontrunning] more on ENS

Ethereum Naming Service (ENS)\footnote{\url{https://ens.domains/}}, the most popular decentral naming service uses a sealed auction to purchase new domains with \textit{.eth} extension which can be resolved using any Ethereum web3 compatible browser. Although the implementation uses a sealed auction, \textit{startAuctionsAndBid}, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount. By doing so the front-runner invalidates the original bid.
%e.g: https://etherscan.io/enslookup?q=handshaker.eth
%TODO: ian goberg: private information retrieval . talk about domain name frontrunning in the traditional sense and how goDaddy can steal the domain when queried for availablity. however in blockchain the queiry is private and does not reveal the intention that you want to buy the domain. View only / solidity code on how to enable this

>>>>

Ethereum Naming Service (ENS)\footnote{\url{https://ens.domains/}}, the most popular decentral naming service uses a sealed auction to purchase new domains with \textit{.eth} extension which can be resolved using any Ethereum web3 compatible browser. Although the implementation uses a sealed auction, \textit{startAuctionsAndBid}, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount. By doing so the front-runner invalidates the original bid. This is similar to traditional domain squatting where the service provider maliciously buys the domains upon domain availably check and before the user gets the chance to finish his order. Although the exact same attack is not feasible on blockchain naming services as querying already registered domains are instant and without leaking any information of the intention of the user to the network.
%e.g: https://etherscan.io/enslookup?q=handshaker.eth
%TODO: ian goberg: private information retrieval . talk about domain name frontrunning in the traditional sense and how goDaddy can steal the domain when queried for availablity. however in blockchain the queiry is private and does not reveal the intention that you want to buy the domain. View only / solidity code on how to enable this
